Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-13 files/Chapter4/SuspendedBeamModel.tex
chapter 4

\documentclass[../../main.tex]{subfiles}
\begin{document}
\setcounter{chapter}{4}
\section{Suspended beam model}
The suspended Timoshenko beam model is referred to as Problem T-3 in this \ref{ssec:1D_Model:ModelProblems}. The beam is suspended at both endpoints by linear springs. The boundary conditions of Problem T-3 as given in section \ref{ssec:1D_Model:ModelProblems} can be rewritten by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D}.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\subsection{Suspended beam model}
In the article \cite{SP06}, the beam is suspended at both ends. The beam is then vibrated and the induced motion causes the beam to transition into a free-free beam. This subsection is a short description of the suspended beam model.

The suspended Timoshenko beam model is referred to as Problem T-3 in this \ref{ssec:1D_Model:ModelProblems}. The beam is suspended at both endpoints by linear springs. The boundary conditions of Problem T-3 as given in section \ref{ssec:1D_Model:ModelProblems} can be rewritten by substituting the constitutive equations \eqref{eq:1D_Model:ConstitutiveEquations1D} and \eqref{eq:1D_Model:ConstitutiveEquations2D}.
